universities

### 2020-08-10 inst/universities.Rmd
more work

```{r, coerceem}
f <- function(y,supp=TRUE,...){
  jj <- as.data.frame(a)
  jj <- subset(jj,jj$year==y)
  o <- function(v){
  good <- v != "DNP"
     v[good] <- order(v[good],decreasing=TRUE)
     return(v)
     }	
  x <- apply(jj,2,o)
  rownames(x) <- jj[,1]
  x <- x[,3:6]
  if(supp){
    return(ordertable2supp(x,...))
  } else {
  return(as.data.frame(x))
  }		
}
f(2012)
```

Now:
```{r,playerwithadvantage}
H <- f(2013) + f(2014) + f(2015)                          # pre  2016
H1 <- H + f(2016) + f(2017) + f(2018) + f(2019) + f(2020) # post 2016
```

Object `H1` is simply the support function for the universities'
strenghts for observations (assumed to be independent) 2013-2020:

```{r}
maxp(H)
```

@@

```{r}
pnames(H) <- c(pnames(H),"S")
H2 <- H + pwa(f(2016),"AUT") + pwa(f(2017),"AUT") +
          pwa(f(2018),"AUT") + pwa(f(2019),"AUT") +
  	  pwa(f(2020),"AUT")
head(H2)
```

Object `H2` is a support function for the Bradley-Terry strengths of
the universities, but with AUT having extra strength `S` post-2016.
We can test the null that `S=0` using package idiom
\code{specificp.test()}:

```{r}
specificp.test(H2,"S",0)
```

@@

>>>>

```{r, label=definehelperfunctionf}
f <- function(a,y){
  a <- subset(a,a$year==y)
  o <- function(v){  # 'v' is a character vector
    good <- v != "DNP"
    v[good] <- rank(-as.numeric(v[good]),ties.method="last")
    return(v)
  }
  out <- data.frame(o(a[,3]),o(a[,4]),o(a[,5]),o(a[,6]),o(a[,7]))
  colnames(out) <- colnames(a)[3:7]
  rownames(out) <- a[,1]
  return(out)
}
f(a,2012)
```

Now:
```{r,playerwithadvantage}
H <- hyper2(pnames=a[1:8,1])
for(i in 2013:2020){ H %<>% `+`(ordertable2supp(f(a,i)))}
H
```

Object `H` is simply the support function for the universities'
strengths for all years' observations (assumed to be independent)
2013-2020:

```{r,label=maxpcalc,cache=TRUE}
m <- maxp(H)
m
pie(m)
```

@@

```{r,label=preandpost}

H1 <- hyper2(pnames=c("AUT_pre",a[c(1:2,4:8),1]))
for(i in 2012:2016){
  b <- f(a,i)
  rownames(b)[3] <- "AUT_pre"
  H1 <- combine(H1,ordertable2supp(b))
} # column loop closes

H2 <- hyper2(pnames=c("AUT_post",a[c(1:2,4:8),1]))
for(i in 2017:2020){
  jj <- f(a,i)
  rownames(jj)[3] <- "AUT_post"
  H2 <- combine(H2,ordertable2supp(jj))
}
maxp(H2)
```

@@

```{r}
H <- combine(H1,H2)
maxp(H)
samep.test(H,c(1,9))
```
